Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2022-11-24 beap_pres_dec2022/beap_pres_dec.tex
Nov 23 from server
November 23 - beap pres updates last of the day

>>>>

		\begin{alertblock}{Homorepeats}
			Consecutive iterations of a single residue
		\end{alertblock}

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{poyglut.png}
		\end{center}

		\begin{alertblock}{Direpeats}
			Consecutive iterations of two ordered, different residues
		\end{alertblock}

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{direpeat.png}
		\end{center}

		\begin{alertblock}{Tandem Repeats}
			Sequence of residues which are repeated a number of times
		\end{alertblock}

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{tandem.png}
			\includegraphics[width=5cm, height=1cm]{tandem.png}
		\end{center}
